Differential invariant signatures for planar Lie group transformations of images

### 2019-08-22 paper/newpaper.tex
newpaper.tex

An algorithm to compute invariants and determine complete signature sets is described in \cite{olver2001}. First, the
entire set of invariants is computed using the method of moving frames. Second, determine the differential invariant order $s$ of $f$. Then the signature set of a maximal set of functionally independent invariants of order $s+1$ is complete. A third step is possible, in which the dimension of the signature set is reduced by eliminating those invariants whose values can be computed from the values of derivatives of some subset of the invariants.

@@

Is this helpful? 
\begin{figure}
\begin{center}
\begin{tikzpicture}[node distance=1.5cm]
\node(C1) [] {Diff};
\node(C2) [below left of=C1] {$\mathrm{Diff}_{\mathrm{vol}}$};
\node(C3) [below right of=C1] {$\mathrm{Diff}_{\mathrm{con}}$};
\node(A1) [below right of=C3]                          {$PSL(2,\mathbb{C})$};
\node(B1)    [below of=C2]    {$PSL(3,\mathbb{R})$};
\node(B2)   [below of=B1]              {$A(2)$};
\node(A2)       [below left of=A1]          {Sim$(2)$};
\node(A3)      [right of=A2]              {$PSL(2,\mathbb{R})$};
\node(B3)   [below of=B2]            {$SA(2)$};
\node(A4)      [below of=A2]            {$E(2)$};
\node(A5) [below right of=A4]{Translation};

>>>>

An algorithm to compute invariants and determine complete signature sets is
described in \cite{olver2001}. First, the entire set of invariants is
computed using the method of moving frames. Second, determine the
differential invariant order $s$ of $f$ \todo[inline]{we need to define the differential invariant order}. Then the signature set of a maximal
set of functionally independent invariants of order $s+1$ is complete. A
third step is possible, in which the dimension of the signature set is
reduced by eliminating those invariants whose values can be computed from the
values of derivatives of some subset of the invariants.

@@

Is this helpful? 
\todo[inline]{Yes, this is helpful but not quite correct yet - $SE(2)$ is missing, and we need edges from $\text{Diff}_{\text{vol}}$ to the special affine and Euclidean groups}
\todo[inline]{Other notes: should our projective group be $PGL(3, \mathbb{R})$ rather than $PSL(3, \mathbb{R})$? or am I confused?}
\begin{figure}
\begin{center}
\begin{tikzpicture}[node distance=1.5cm]
\node(C1) [] {Diff};
\node(C2) [below left of=C1] {$\mathrm{Diff}_{\mathrm{vol}}$};
\node(C3) [below right of=C1] {$\mathrm{Diff}_{\mathrm{con}}$};
\node(A1) [below right of=C3]                          {$PSL(2,\mathbb{C})$};
\node(B1)    [below of=C2]    {$PSL(3,\mathbb{R})$};
\node(B2)   [below of=B1]              {$A(2)$};
\node(A2)       [below left of=A1]          {Sim$(2)$};
\node(A3)      [right of=A2]              {$PSL(2,\mathbb{R})$};
\node(B3)   [below of=B2]            {$SA(2)$};
\node(A4)      [below of=A2]            {$E(2)$};
\node(A5) [below right of=A4]{Translation};
